Fast and Error-Adaptive Influence Maximization based on Count-Distinct Sketches

### 2022-01-25 paper.tex
Update on Overleaf.

\documentclass[10pt,journal,compsoc]{IEEEtran}
\usepackage{subfiles}
\usepackage{url}
\usepackage[pdftex]{graphicx}
\usepackage{amsmath}
\usepackage{xspace}
\usepackage{multirow}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage{subfig}
\usepackage[noend]{algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:~}}
\renewcommand{\algorithmicensure}{\textbf{Output:~}}
\newcommand\ovr[1]{\overrightarrow{#1}}
\newcommand\myeq{\mkern1.5mu{=}\mkern1.5mu}
\usepackage{booktabs}
\usepackage{array}
\usepackage{color}
\usepackage{listings}
\usepackage{placeins}
\usepackage{enumitem}
\usepackage{balance}

%%%%%%
% notation 
%%%%%
\ifCLASSOPTIONcompsoc
  \usepackage[nocompress]{cite}
\else
  \usepackage{cite}
\fi

\ifCLASSINFOpdf
\else
\fi
\newcommand\ggx[1]{\textcolor{blue}{#1}}

\newcommand\MYhyperrefoptions{bookmarks=true,bookmarksnumbered=true,
pdfpagemode={UseOutlines},plainpages=false,pdfpagelabels=true,
colorlinks=true,linkcolor={black},citecolor={black},urlcolor={black},
pdftitle={Bare Demo of IEEEtran.cls for Computer Society Journals},%<!CHANGE!
pdfsubject={Typesetting},%<!CHANGE!
pdfauthor={Gokhan Gokturk, Kamer Kaya},%<!CHANGE!
pdfkeywords={Influence Maximization, Graph Processing, Graph Sampling, Fused Sampling, Memory Access Regularization, Count-Distinct Sketch}}%<^!CHANGE!

\newcommand\acro{{\sc{HyperFuseR\xspace}\xspace}\xspace}
\usepackage{xcolor}
\newcommand\kktodo[1]{\textcolor{red}{#1}}

\newcommand\minspeedup{{{3.5\xspace}\xspace}\xspace}
\newcommand\maxspeedup{{{11\xspace}\xspace}\xspace}

\newcommand\maxspeedupTIM{{{1500\xspace}\xspace}\xspace}
\newcommand\maxspeedupIMM{{{27.87\xspace}\xspace}\xspace}
\newcommand\maxspeedupSKIM{{{11\xspace}\xspace}\xspace}

@@

\title{Fast and Error-Adaptive Influence Maximization based on Count-Distinct Sketches}

\author{G\"{o}khan~G\"{o}kt\"{u}rk
        and~Kamer~Kaya% <-this % stops a space
\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem G. G\"{o}kt\"{u}rk and K. Kaya are with Computer Science and Engineering, Faculty of Engineering and Natural Sciences, Sabanci University, TR~34956, Istanbul, Turkey.}% <-this % stops a space
%\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}
}
%FIXME

% \markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
% {Shell \MakeLowercase{\textit{et al.}}: Bare Advanced Demo of IEEEtran.cls for IEEE Computer Society Journals}

\IEEEtitleabstractindextext{%
\begin{abstract}
Influence maximization~(IM) is the problem of finding a seed vertex set that maximizes the expected number of vertices influenced under a given diffusion model. Due to the NP-Hardness of finding an optimal seed set, approximation algorithms are frequently used for IM. 
% In addition to these high-quality yet expensive approximation algorithms, lightweight, sketch-based approaches which do not step-by-step simulate the diffusion process have been proposed in the literature to cope with the scale of today's networks. 
In this work, we describe a fast, error-adaptive approach that leverages Count-Distinct sketches and hash-based fused sampling. To estimate the number of influenced vertices throughout a diffusion, we use per-vertex Flajolet-Martin sketches where each sketch corresponds to a sampled subgraph. To efficiently simulate the diffusions, the reach-set cardinalities of a single vertex are stored in memory in a consecutive fashion. This allows the proposed algorithm to estimate the number of influenced vertices in a single step for simulations at once. %In addition, thanks to their efficiency, and the scalability of our parallel implementation, we can rebuild the sketches whenever it is necessary. 
For a faster IM kernel, we rebuild the sketches in parallel only after observing estimation errors above a given threshold. Our experimental results show that the proposed algorithm yields high-quality seed sets while being up to $119\times$ faster than a state-of-the-art approximation algorithm. In addition, it is up to $62\times$ faster than a sketch-based approach while producing seed sets with $3\%$--$12\%$ better influence scores.
\end{abstract}
}

% Note that keywords are not normally used for peer review papers.
% section 3, overview
% 
% 
% 
% 
% 
% 
% 
% 
%

\maketitle

\IEEEdisplaynontitleabstractindextext
\IEEEpeerreviewmaketitle

\ifCLASSOPTIONcompsoc
\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
\else
\section{Introduction}
\label{sec:introduction}
\fi

@@

\item We evaluate the runtime performance, memory consumption, and influence score of sketch- and approximation-based state-of-the-art influence maximization algorithms, namely {\sc Skim}~\cite{cohen2014sketch}, {\sc Tim+}~\cite{tim} and {\sc Imm}~\cite{minutoli2019fast}, to accurately position the performance of \acro{} within the IM literature. The experiments show that \acro can be $62\times$ and $119\times$ faster than a state-of-the-art sketch-based and approximation algorithm, respectively while reaching the influence quality of the accurate algorithms with less memory.

@@

\begin{table}[!ht]
    \caption{Table of notations}
    \label{tab:notation}
    \centering
    \begin{tabular}{|l|p{0.7\linewidth}|}
        \hline
        Variable & Definition  \\
        \hline
        %\kktodo{uzerinden 
        %gecelim}\ggx{A ekledim, S' uygun olur mu karar veremedim.}\\
        $G = (V,E)$     & Graph $G$ with vertices $V$ and edges $E$ \\
         $\Gamma^+_G(u)$ & The set of vertices $v$ where $(u,v) \in E$ \\ %%FIXME
        $\Gamma^-_G(u)$  &The set of vertices $v$ where $(v, u) \in E$\\ %%FIXME
        $w_{u,v}$       & Probability of $u$ directly influencing $v$ \\
        %$SCC(v) $       & Strongly connected component of vertex $v$\\
        $R_{G}(v)$      & Reachability set of vertex $v$ on graph $G$\\
%        $\overline{R_{G}(v)} & Complement of the vertex set $R_{G}(v)$\\
        \hline\hline
        $S$             & Seed set to maximize influence\\
        $K$             & Size of the seed set\\
        ${\cal J}$   & Number of Monte-Carlo simulations performed\\
        $\sigma_{G}(S)$ & The influence score of $S$ in $G$, i.e., expected number of vertices reached from $S$ in $G$\\
        % $\sigma_{G}{(S,v)}$          & Marginal influence gain by adding vertex $v$ to seed set $S$\\
        \hline\hline
        $w_{u,v}$             & Sampling probability for the edge $(u,v)$\\
        $P(s,v)_r $     & Random probability generated for selecting edge vertices $s$ to $v$ in simulation $r$\\
        $h(u,v)$        & Hash function for edge $\{u,v\}$\\
        $h_{max}$       & Maximum value hash function $h$ can return\\
        %$X_r$           & Random number/hash generated for simulation $r$  \\
        \hline\hline
        $e$             & Estimated reachability set size\\
        % $[a, \ldots, a]_B$      & Vector of size $B$, contains all $a$\\
        $M_u[j]$        & $j$th sketch register for vertex $u$\\
        $\varsigma $    & Influence gained before last sketch build\\
        $\sigma $       & Influence Score\\
        $\delta$        & Marginal gain after last sketch build\\
        $err_l$         & Local estimation error of the sketch\\
        $err_g$         & Global estimation error of the sketch\\
        $\epsilon_{g}$    & Global estimation error threshold\\
        $\epsilon_{l}$    & Local estimation error threshold\\ 
        $\epsilon_{c}$    & Non-convergenced vertex threshold\\
      %  $x[[i, j]]$   & Slice of vector  $x$ between indices $i$ and $j$, not including $j$ \\ 
        \hline         
    \end{tabular}
\end{table}
\subsection{Influence Maximization}

@@

\begin{figure}[!ht] 
    \centering
  \subfloat[\small{IC}\label{fig:ic}]{%
       \includegraphics[width=0.37\linewidth]{images/ic.pdf}}
  \subfloat[\small{WC}\label{fig:wc}]{%
        \includegraphics[width=0.37\linewidth]{images/wc.pdf}}
    \\% IMAGES HERE
  \caption{\small{\protect\subref{fig:ic} 
The directed graph $G = (V, E)$ for IC with independent diffusion probabilities. 
\protect\subref{fig:wc}
The directed graph for WC is obtained by setting the diffusion probabilities of incoming edges to $1 / |\Gamma^-_G(v)|$ for each vertex $v \in V$.% \kktodo{bu (4,1) kenarinin agirligi 1 degil mi?}\ggx{done.} 
  }}
  %\label{fig_ic_model} 
  \label{fig:xx} 
\end{figure}

@@

\item{\bf Linear threshold} generalizes the IC model and activates the vertex $v$ once the cumulative activation coming from its neighbors exceeds a given threshold $\theta_v$. 
All the $(u, v)$ edges with active $u$ vertices are taken into account in the process. Vertex $v$ is activated when the total activation probability through these edges exceeds $\theta_v$~\cite{kempe2003maximizing}.  
%Therefore, the independent cascade model is a special variant of the LT model with $\theta_v = 0$. 
\end{itemize}

@@

\subsection{Count-Distinct Sketches}\label{sec:sketch}
The {\em distinct element count} problem focuses on finding the number of distinct elements in a stream where the elements are coming from a universal set ${\cal U}$. Finding the number of vertices to be influenced of a candidate seed vertex $u$, i.e., the cardinality of $u$'s {\em reachability set}, is a similar problem. For each sample subgraph, the number of visited vertices is found while traversing the subgraphs starting from $u$. Note that an exact computation of set cardinality requires memory proportional to the cardinality, which is ${\mathcal O}(|{\cal U}|)$.

@@

For directed graphs, storing reachability sets for all vertices and merging these sets are infeasible for nontrivial graphs. 
If one-hot vectors are used to store the reachability sets for constant insertion time, $\mathcal{O}(n^2\mathcal{R})$ bits of memory is required where each merge operation has $\mathcal{O}(n)$ time complexity. 
If disjoints sets are used for storing reachability sets; $\mathcal{O}(n{\sigma}\mathcal{R})$ 
%\kktodo{Gokhan bunu aciklayalim, bir de $\bar{\sigma}$ nedir}\ggx{estimated influence} 
memory is required to store all reachability sets, and each merge operation has $\mathcal{O}({\tt Ack}(\sigma))$ complexity where ${\tt Ack}$ is the Ackermann~\cite{ackermann} function. %\kktodo{bu Ackermann'a atif verelim}.\ggx{done.}

Count-Distinct Sketches can be leveraged to estimate reachability sets' cardinality efficiently; for instance, the Flajolet–Martin~(FM) sketch~\cite{flajolet1985probabilistic} can do this with a constant number, ${\cal J}$, of registers. Furthermore, the union of two sketches can be computed in constant time. The FM sketch stores that how rare the elements are in a stream. The rarity of the elements is estimated by counting the maximum number of leading zeros in the stream elements' hash values. Initially, each register is initialized with zero. The items are hashed one by one, and the length of the longest all-zero prefix is stored in the register. With a single register, the cardinality estimation can be done by computing the power $2^\ell$ where $\ell$ is the value in the register.

In practice, multiple registers and hash values, $M[j]$ and $h_j$, are commonly used to reduce variance. For a sketch with multiple registers, the impact of adding an item $x \in \cal{U}$ is shown in~\eqref{eq:sketch-add}:
\begin{equation}
    \label{eq:sketch-add}
    M[j] = \max(M[j], clz(h_j(x)),~1 \leq j \leq {\cal J}
\end{equation} where $clz(y)$ returns the number of leading zeros in $y$ and ${\cal J}$ is the number of sketch registers. With multiple registers, the average of the register values can be used to estimate the cardinality, and the result is divided to a correction factor $\phi \approx 0.77351$ to fix the error due to hash collisions. That is the estimated cardinality $e$ is computed as
\begin{equation}
    \label{eq:sketch-estimate}
    e = 2^{\bar{M}}/\phi
\end{equation} 
where $\bar{M} = {\tt{avg}}_j\{M[j]\}$ is the mean of the register values.

@@

\acro first performs a diffusion process; the process starts with per-vertex sketches that are initialized with the hash value of the corresponding vertex~(i.e., every vertex reaches to itself). Then, for all the (sampled) edges ($u, v$), i.e., the ones that contribute to the diffusion for this simulation, the sketch of the source vertex $u$ is merged into that of the target vertex $v$ until all sketch registers for all the vertices converge. The merge operation utilized in this process is slightly different from the conventional one and retrofitted to mimic the IC diffusion.

@@

After estimating the reachability set cardinalities, \acro picks the vertex $v$ with the largest cardinality by evaluating the sketches. Then it finds the (actual) reachability set of the latent seed set, which is the union of the reachability sets of $v$ and the vertices in the seed set, by performing Monte-Carlo simulations. The vertices in this reachability set are removed from the live set $L$. %labeled as {\em visited}. 
%\kktodo{niye blocked, influenced desek?}\ggx{literaturde kullanilan terim o sekilde, ben visited'i tercih ederdim, algorithmaya gore live set L den çıkartıyoruz diye güncelledim.} 
Hence, in later iterations, these vertices will not contribute to the marginal gain. Finally, the algorithm checks if rebuilding is necessary for the sketches based on the difference between the sketch estimate and Monte-Carlo estimate. %\kktodo{yukaridaki cumlelerde bunlara isim verelim, burada soyleyelim matematiksel olarak - zaten isimleri var sanirim}.\ggx{malesef sembolleri,isimleri yok. $u \notin R_S$ şeklinde.}

\subsection{Hash-based Fused Sampling}
The probabilistic nature of cascade models requires sampling subgraphs from $G = (V, E)$ to simulate the diffusion process. If performed individually as a preprocessing step, as the literature traditionally does, sampling can be an expensive stage, furthermore, a time-wise dominating one for the overall IM kernel. We identify two main bottlenecks; first, sampling multiple sub-graphs may demand multiple passes on the graph, which can be very large and expensive to stream to the computational cores, and second, if samples are memoized, the memory requirement can be a multiple of the graph size. 
In this work, we borrow the fused-sampling technique from {\sc InFuseR}~\cite{infuser} which eliminates the necessity of creation and storage of the sample subgraphs in memory. 
In Fig.~\ref{fig:traversal}, we briefly illustrate fused-sampling; instead of processing the samples independently as in Fig.~\ref{fig:sims}, fused-sampling processes each edge concurrently for multiple simulations as shown in Fig.~\ref{fig:fused}. This allows us to process each edge only a few times instead of once for every simulation.

\begin{figure}[!ht] 
    \centering
    %\subfloat[\label{fig:toy}]{%
    %   \includegraphics[width=0.47\linewidth]{sims-a%}}%  \\
    \subfloat[\label{fig:sims}]{%
        \includegraphics[width=0.5\linewidth]{images/samples.pdf}
    } 
    \subfloat[\label{fig:fused}]{%
     \includegraphics[width=0.5\linewidth]{images/fused.pdf}}
  \caption{\small{
  %\protect\subref{fig:toy} The toy graph 
  \protect\subref{fig:sims} Two sampled subgraphs of the toy graph from Figure~\ref{fig:ic} with 4 vertices and 6 edges.
  \protect\subref{fig:fused} The simulations performed are fused with sampling. Each edge is labeled with the corresponding sample/simulation IDs. 
  }}
  \label{fig:traversal} 
\end{figure}

In \acro, when an edge of the original graph is being processed, it is processed for all possible samples. Then, it is decided to be {\it sampled} or {\it skipped} depending on the outcome of the hash-based random value for each sample. Given a graph $G = (V, E)$, for an edge $(u, v) \in E$, the hash function used is given below:
\begin{equation}
    \label{eq:hash}
    h(u,v) = \mbox{{\sc Murmur3}}(u||v)~mod~2^{31}  
\end{equation}
where $||$ is the concatenation operator. In our preliminary experiments, we have tried a set of hash algorithms. After a careful analysis, we chose {{\sc Murmur3}} due to its simplicity and good avalanche behavior with a maximum bias $0.5\%$~\cite{MurmurHash3Performance}. Although the approach mentioned above generates a unique hash value for each edge, and hence a unique sampling probability, different simulations require different probabilities. First, a set of uniformly randomly chosen numbers $X_r \in_R [0, h_{max}]$ associated with each simulation $r$ are generated to enable this for each edge. Then the sampling probability of $(u, v)$ for simulation $r$, $P(u, v)_r$, is computed: To do this, the hash value, $h(u,v)$, is XOR'ed with  $X_r$ and the result is normalized by dividing the value to the upper limit of the hash value $h_{max}$. Formally,
\begin{equation}
    \label{eq:hash_prob}
    P(u,v)_r = \frac{X_r \oplus h(u,v)}{h_{max}}.
\end{equation}
% The edge $\{u,v\}$ is verified to be in the sample if ${\rho}(u,v)_r$ is smaller than or equal to the threshold $w_{u,v}$. 
The edge $(u,v)$ exists in the sample $r$ if and only if  ${P}(u,v)_r$ is smaller than the edge threshold $w_{u,v}$. One of this approach's benefits is that an edge can be sampled using a single XOR and compare-greater-than operation. Moreover, the corresponding control flow branch overhead can be removed using {\em conditional move} instructions.

\begin{figure}[!ht] 
    \centering
    \includegraphics[width=1\linewidth]{./images/CDF.pdf}
    \caption{\small{Cumulative probability function of hash-based sampling probabilities on various real-life networks.}}
    \label{fig:prob-cdf} 
\end{figure}

>>>>

\documentclass[review]{elsarticle}
\usepackage{subfiles}
\usepackage{url}
\usepackage{amsmath}
\usepackage{xspace}
\usepackage{multirow}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage{subfig}
\usepackage[noend]{algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:~}}
\renewcommand{\algorithmicensure}{\textbf{Output:~}}
\newcommand\ovr[1]{\overrightarrow{#1}}
\newcommand\myeq{\mkern1.5mu{=}\mkern1.5mu}
\usepackage{booktabs}
\usepackage{array}
\usepackage{color}
\usepackage{listings}
\usepackage{placeins}
\usepackage{enumitem}
\usepackage{balance}
\usepackage{etoolbox}
\usepackage{lineno,hyperref}
\newcommand\acrotwo{
\multirow{2}{*}{ \shortstack{ \sc{Hyp.}\\\sc{Fus.}} }
}
\renewcommand{\toprule}{}
\newcommand\acro{{\sc{HyperFuseR\xspace}\xspace}\xspace}
\newcommand\kktodo[1]{\textcolor{red}{#1}}
\newcommand\minspeedup{{{3.5\xspace}\xspace}\xspace}
\newcommand\maxspeedup{{{11\xspace}\xspace}\xspace}
\newcommand\maxspeedupTIM{{{1500\xspace}\xspace}\xspace}
\newcommand\maxspeedupIMM{{{27.87\xspace}\xspace}\xspace}
\newcommand\maxspeedupSKIM{{{11\xspace}\xspace}\xspace}

\let\oldbibliography\thebibliography
\renewcommand{\thebibliography}[1]{%
  \oldbibliography{#1}%
  \setlength{\itemsep}{0pt}%
}

\modulolinenumbers[5]

\renewcommand{\floatpagefraction}{.98}
\journal{Journal of Parallel and Distributed Computing}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{frontmatter}
\title{Fast and Error-Adaptive Influence Maximization based on Count-Distinct Sketches}%\tnoteref{t1,t2}}

%% Group authors per affiliation:
%% or include affiliations in footnotes:
\author[add]{Gökhan Göktürk}
\ead{gokhan.gokturk@sabanciuniv.edu}

\author[add]{Kamer Kaya}
\ead{kaya@sabanciuniv.edu}

\address[add]{Faculty of Engineering and Natural Sciences, Sabancı University, Turkey}

% \IEEEtitleabstractindextext{%
\begin{abstract}
Influence maximization~(IM) is the problem of finding a seed vertex set that maximizes the expected number of vertices influenced under a given diffusion model. Due to the NP-Hardness of finding an optimal seed set, approximation algorithms are frequently used for IM. 
% In addition to these high-quality yet expensive approximation algorithms, lightweight, sketch-based approaches which do not step-by-step simulate the diffusion process have been proposed in the literature to cope with the scale of today's networks. 
In this work, we describe a fast, error-adaptive approach that leverages Count-Distinct sketches and hash-based fused sampling. To estimate the number of influenced vertices throughout a diffusion, we use per-vertex Flajolet-Martin sketches where each sketch corresponds to a sampled subgraph. To efficiently simulate the diffusions, the reach-set cardinalities of a single vertex are stored in memory in a consecutive fashion. This allows the proposed algorithm to estimate the number of influenced vertices in a single step for simulations at once. %In addition, thanks to their efficiency, and the scalability of our parallel implementation, we can rebuild the sketches whenever it is necessary. 
For a faster IM kernel, we rebuild the sketches in parallel only after observing estimation errors above a given threshold. Our experimental results show that the proposed algorithm yields comparable seed sets while being up to $3,337\times$ faster than a state-of-the-art, high-quality influence maximization algorithm. In addition, it is up to $63\times$ faster than a sketch-based approach while producing seed sets with $2\%$--$10\%$ better influence scores.
\end{abstract}
% } 
\begin{keyword}
Influence Maximization, Graph Processing, Graph Sampling, Fused Sampling, Memory Access Regularization, Count-Distinct Sketch
\end{keyword}
\end{frontmatter}

\section{Introduction}

@@

\item We evaluate the runtime performance, memory consumption, and influence score of sketch- and approximation-based state-of-the-art influence maximization algorithms, namely {\sc Skim}~\cite{cohen2014sketch}, {\sc SSA}~\cite{nguyen2016stop}, {\sc Tim+}~\cite{tim} and {\sc Imm}~\cite{minutoli2019fast}, to accurately position the performance of \acro{} within the IM literature. The experiments show that \acro can be $63\times$ and $3337\times$ faster than a state-of-the-art sketch-based and high-quality approximation algorithm, respectively while reaching the influence quality of the accurate algorithms with less memory.

@@

\begin{table}[!ht]
    \caption{Table of notations}
    \label{tab:notation}
          \renewcommand*{\arraystretch}{0.6}
    \centering
        \begin{small}
    % \tiny
    \begin{tabular}{|l|p{0.7\linewidth}|}
        \hline
        Variable & Definition  \\
        \hline
        %\kktodo{uzerinden 
        %gecelim}\ggx{A ekledim, S' uygun olur mu karar veremedim.}\\
        $G = (V,E)$     & Graph $G$ with vertices $V$ and edges $E$ \\
        $N$ & Number of vertices\\
        $M$ & Number of edges\\
        $T$ & Depth of the graph\\
        $\Gamma^+_G(u)$ & The set of vertices $v$ where $(u,v) \in E$ \\ %%FIXME
        $\Gamma^-_G(u)$  &The set of vertices $v$ where $(v, u) \in E$\\ %%FIXME
        $w_{u,v}$       & Probability of $u$ directly influencing $v$ \\
        %$SCC(v) $       & Strongly connected component of vertex $v$\\
        $R_{G}(v)$      & Reachability set of vertex $v$ on graph $G$\\
%        $\overline{R_{G}(v)} & Complement of the vertex set $R_{G}(v)$\\
        \hline\hline
        $S$             & Seed set to maximize influence\\
        $K$             & Size of the seed set\\
        ${\cal J}$   & Number of Monte-Carlo simulations performed\\
        $\sigma_{G}(S)$ & The influence score of $S$ in $G$, i.e., expected number of vertices reached from $S$ in $G$\\
        % $\sigma_{G}{(S,v)}$          & Marginal influence gain by adding vertex $v$ to seed set $S$\\
        \hline\hline
        $w_{u,v}$             & Sampling probability for the edge $(u,v)$\\
        $P(s,v)_r $     & Random probability generated for selecting edge vertices $s$ to $v$ in simulation $r$\\
        $h(u,v)$        & Hash function for edge $\{u,v\}$\\
        $h_{max}$       & Maximum value hash function $h$ can return\\
        %$X_r$           & Random number/hash generated for simulation $r$  \\
        \hline\hline
        $e$             & Estimated reachability set size\\
        % $[a, \ldots, a]_B$      & Vector of size $B$, contains all $a$\\
        $M_u[j]$        & $j$th sketch register for vertex $u$\\
        $\varsigma $    & Influence gained before last sketch build\\
        $\sigma $       & Influence Score\\
        $\delta$        & Marginal gain after last sketch build\\
        $err_l$         & Local estimation error of the sketch\\
        $err_g$         & Global estimation error of the sketch\\
        $\epsilon_{g}$    & Global estimation error threshold\\
        $\epsilon_{l}$    & Local estimation error threshold\\ 
        $\epsilon_{c}$    & Non-convergenced vertex threshold\\
      %  $x[[i, j]]$   & Slice of vector  $x$ between indices $i$ and $j$, not including $j$ \\ 
        \hline         
    \end{tabular}
    \end{small}
\end{table}
\FloatBarrier
\subsection{Influence Maximization}

@@

\begin{figure}[!ht] 
    \centering
  \subfloat[\small{IC}\label{fig:ic}]{%
       \includegraphics[width=0.26\linewidth]{images/ic.pdf}}
  \subfloat[\small{WC}\label{fig:wc}]{%
        \includegraphics[width=0.26\linewidth]{images/wc.pdf}}
    \\% IMAGES HERE
  \caption{\small{\protect\subref{fig:ic} 
The directed graph $G = (V, E)$ for IC with independent diffusion probabilities. 
\protect\subref{fig:wc}
The directed graph for WC is obtained by setting the diffusion probabilities of incoming edges to $1 / |\Gamma^-_G(v)|$ for each vertex $v \in V$.% \kktodo{bu (4,1) kenarinin agirligi 1 degil mi?}\ggx{done.} 
  }}
  %\label{fig_ic_model} 
  \label{fig:xx} 
\end{figure}

@@

\item{\bf Linear Threshold} model generalizes the IC model and activates the vertex $v$ once the cumulative activation coming from its neighbors exceeds a given threshold $\theta_v$. 
All the $(u, v)$ edges with active $u$ vertices are taken into account in the process. Vertex $v$ is activated when the total activation probability through these edges exceeds $\theta_v$~\cite{kempe2003maximizing}.  
%Therefore, the independent cascade model is a special variant of the LT model with $\theta_v = 0$. 
\end{itemize}

@@

\subsection{Count-Distinct Sketches}\label{sec:sketch}
The {\em distinct element count} problem focuses on finding the number of distinct elements in a stream where the elements are coming from a universal set ${\cal U}$. Finding the number of vertices to be influenced of a candidate seed vertex $u$, i.e., the cardinality of $u$'s {\em reachability set}, is a similar problem. For each sample subgraph, the number of visited vertices is found while traversing the subgraphs starting from $u$. Note that an exact, linear-time computation of stream cardinality requires memory proportional to the universal set cardinality, i.e., ${\Theta}(|{\cal U}|)$.

@@

For directed graphs, storing reachability sets for all vertices and merging these sets are infeasible for nontrivial graphs. 
If one-hot vectors are used to store the reachability sets for constant insertion time, $\Theta(n^2\mathcal{R})$ bits of memory is required where each merge operation has $\Theta(n)$ time complexity. 
If disjoints sets are used for storing reachability sets; $\mathcal{O}(n{\sigma}\mathcal{R})$ 
%\kktodo{Gokhan bunu aciklayalim, bir de $\bar{\sigma}$ nedir}\ggx{estimated influence} 
memory is required to store all reachability sets, and each merge operation has $\mathcal{O}({\tt Ack}(\sigma))$ complexity where ${\tt Ack}$ is the Ackermann~\cite{ackermann} function. %\kktodo{bu Ackermann'a atif verelim}.\ggx{done.}

Count-Distinct Sketches can be leveraged to estimate a reachability set's cardinality efficiently; for instance, the Flajolet–Martin~(FM) sketch~\cite{flajolet1985probabilistic} uses a constant number, ${\cal J}$, of registers where ${\cal J}$ can be increased for better estimates. Furthermore, the union of two sketches can be computed in constant time which is a necessary property for an efficient estimation of reachability set cardinalities. The essence of an FM sketch is that it keeps the track of how rare the elements are in a stream. The rarity of the stream is estimated by counting the maximum number of leading zeros in the stream elements' hash values. Initially, each register is initialized with zero. The items are hashed one by one, and the length of the longest all-zero prefix is stored in the register. With a single register, the cardinality estimation can be done by computing the power $2^r$ where $r$ is the value in the register.

In practice, multiple, ${\mathcal J}$, registers and hash values, $M[j]$ and $h_j$, $1 \leq j \leq {\cal J}$, are used to reduce the variance of the estimation. For a sketch with multiple registers, the impact of adding an item $x \in \cal{U}$ is shown in~\eqref{eq:sketch-add}:
\begin{equation}
    \label{eq:sketch-add}
    M[j] = \max(M[j], clz(h_j(x)),~1 \leq j \leq {\cal J}
\end{equation} where $clz(y)$ returns the number of leading zeros in $y$ and ${\cal J}$ is the number of sketch registers. With multiple registers, the average of the register values can be used to estimate the cardinality, and the result is divided to a correction factor $\phi \approx 0.77351$ to fix the error due to hash collisions. That is the estimated cardinality $e$ is computed as
\begin{equation}
    \label{eq:sketch-estimate}
    e = 2^{\bar{M}}/\phi
\end{equation} 
where $\bar{M} = {\tt{avg}}_j\{M[j]\}$ is the mean of the register values.

@@

\acro first performs a diffusion process; the process starts with per-vertex sketches that are initialized with the hash value of the corresponding vertex~(i.e., every vertex reaches to itself). Then, for all the (sampled) edges ($u, v$), i.e., for the ones that contribute to the diffusion for this simulation, the sketch of the source vertex $u$ is merged into that of the target vertex $v$ until all sketch registers for all the vertices converge. The merge operation utilized in this process is slightly different from the conventional one and retrofitted to mimic the IC diffusion.

@@

After estimating the reachability set cardinalities, \acro picks the vertex $v$ with the largest cardinality by evaluating the sketches. Then it finds the (actual) reachability set of the latent seed set, which is the union of the reachability sets of $v$ and the vertices in the seed set, by performing Monte-Carlo simulations. The vertices in this reachability set are removed from the live set $L$. %labeled as {\em visited}. 
%\kktodo{niye blocked, influenced desek?}\ggx{literaturde kullanilan terim o sekilde, ben visited'i tercih ederdim, algorithmaya gore live set L den çıkartıyoruz diye güncelledim.} 
Hence, in later iterations, these vertices will not contribute to the marginal gain. Finally, the algorithm checks if rebuilding is necessary for the sketches based on the difference between the sketch estimate and Monte-Carlo estimate. The proposed approach and the algorithm will be described in this section in more detail starting with fused sampling.%\kktodo{yukaridaki cumlelerde bunlara isim verelim, burada soyleyelim matematiksel olarak - zaten isimleri var sanirim}.\ggx{malesef sembolleri,isimleri yok. $u \notin R_S$ şeklinde.}

\subsection{Hash-based Fused Sampling}
The probabilistic nature of cascade models requires sampling subgraphs from $G = (V, E)$ to simulate the diffusion process. If performed individually as a preprocessing step, as the literature traditionally does, sampling can be an expensive stage, furthermore, a time-wise dominating one for the overall IM kernel. That is first, sampling multiple sub-graphs may demand multiple passes on the graph, which can be very large and expensive to stream to the computational cores, and second, if samples are memoized, the memory requirement can be a multiple of the graph size. 
In this work, we borrow the fused-sampling technique from {\sc InFuseR}~\cite{infuser} which eliminates the necessity of creation and storage of the sample subgraphs in memory. 
In Fig.~\ref{fig:traversal}, we illustrate fused-sampling; instead of processing the samples independently as in Fig.~\ref{fig:sims}, fused-sampling processes each edge concurrently for multiple simulations as shown in Fig.~\ref{fig:fused}. This allows us to process each edge only a few times instead of once per simulation.

\begin{figure}[!ht] 
    \centering
    %\subfloat[\label{fig:toy}]{%
    %   \includegraphics[width=0.47\linewidth]{sims-a%}}%  \\
    \subfloat[\label{fig:sims}]{%
        \includegraphics[width=0.35\linewidth]{images/samples.pdf}
    } 
    \subfloat[\label{fig:fused}]{%
     \includegraphics[width=0.35\linewidth]{images/fused.pdf}}
  \caption{\small{
  %\protect\subref{fig:toy} The toy graph 
  \protect\subref{fig:sims} Two sampled subgraphs of the toy graph from Figure~\ref{fig:ic} with 4 vertices and 6 edges.
  \protect\subref{fig:fused} The simulations performed are fused with sampling. Each edge is labeled with the corresponding sample/simulation IDs. 
  }}
  \label{fig:traversal} 
\end{figure}

In \acro, when an edge of the original graph is being processed, it is processed for all possible samples. Then, it is decided to be {\it sampled} or {\it skipped} depending on the outcome of the hash-based random value for each sample. Given a graph $G = (V, E)$, for an edge $(u, v) \in E$, the hash function used is given below:
% \begin{equation}
%     \label{eq:hash}
%     h(u,v) = \mbox{{\sc CRC32}}(u||v)~mod~2^{31}  
% \end{equation} %FIXME: does this mean this value be negative?

\begin{equation}
    \label{eq:hash}
    h(u,v) = \mbox{{\sc Hash}}(u||v)~mod~2^{31}  
\end{equation} %FIXME: does this mean this value be negative?
where $||$ is the concatenation operator. In our preliminary experiments, we have tried a set of hash algorithms and found that {\sc Crc32}~\cite{koopman200232} and {{\sc Murmur3}} are good candidates for {\sc Hash}. {{\sc Murmur3}} was slightly faster than {\sc Crc32} with better randomness properties. After a preliminary analysis, we chose {{\sc Murmur3}} due to its simplicity and good avalanche behavior with a maximum bias $0.5\%$~\cite{MurmurHash3Performance}. An  important bottleneck of hash-based fused sampling is the need of the hash value for an edge whenever it is read from the memory. To mitigate its overhead, using $\Theta(|E|)$ more memory, we precompute and memoize the hash values (and read them when we need them). We have also tried recomputing the hash values every time they are needed; this incurred around $5\%$ slowdown. Since {\acro} is designed for multi-core servers, extra $\Theta(|E|)$ memory is a practical overhead. However, considering its low overhead, the recomputation strategy can be promising for memory-restricted accelerators and devices such as GPUs.
